%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contract
% LaTeX Template
% Version 1.0 (December 8 2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Brandon Fryslie
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Note:
% If you are using Apple OS X, go into structure.tex and uncomment the font
% specifications for OS X and comment out the default specifications - this will
% drastically increase how good the document looks. You will now need to
% compile with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,12pt]{article} % The default font size is 12pt on A4 paper, change to 'usletter' for US Letter paper and adjust margins in structure.tex

\input{structure.tex} % Input the structure.tex file which specifies the document layout and style

\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{hyperref}

%----------------------------------------------------------------------------------------
%	DYNAMIC CONTRACT INFORMATION
%----------------------------------------------------------------------------------------

% Your name and company name
\newcommand{\YourName}{
Joseph Armitage \\
Jacob Chamberlain \\
Saba Kia \\
Fides Linga \\
Angela Zavaleta}
\newcommand{\CompanyName}{Team 4}

% Your address
\newcommand{\AddressLineOne}{1265 Military Trail}
\newcommand{\AddressLineTwo}{Scarborough, ON, M1C1A4}

% Your email address
\newcommand{\YourEmail}{
joe.armitage@mail.utoronto.ca \\
 \\
 \\
fides.linga@mail.utoronto.ca \\
angela.zavaleta@mail.utoronto.ca
}

% The client's name
\newcommand{\ClientName}{CSCD01}

% The delivery date for specifications and completion date for the project
\newcommand{\DeliveryDate}{[date]}
\newcommand{\CompletionDate}{[date]}

% Professor's information
\newcommand{\ProfName}{Anya Tafliovich}

% TA's information
\newcommand{\TAName}{Jerry}

% Stand Up Meeting Length
\newcommand{\StandUpLength}{15 minutes} 

% Name of Open Source Project we're working on
\newcommand{\Project}{MatPlotLib}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}

\vspace*{\fill} % Add whitespace above to center the title page content

\begin{center}

{\LARGE Working Agreement for \ClientName ~ Final Project}\\ [1.5cm]

Submitted: \today

\end{center}

\CompanyName \\

\YourName \\

\AddressLineOne \\
\AddressLineTwo \\

\YourEmail

\vspace*{\fill} % Add whitespace below to center the title page content

\end{titlepage}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{Objective}

\CompanyName~(hereafter referred to as the Group) agrees to the following terms of mutual engagement in the \ClientName ~Final Project (hereafter referred to as the Project) with the goal of improving and adding to the source of \Project.

The Professor, \ProfName, of \ClientName~and the Teacher's Assistant, \TAName, (hereafter referred to as the Client) will provide the terms of the Project. This agreement clarifies how the Group will interact with the aim of adherence to those terms.

In order to achieve this goal, the Group will adhere to an Agile development methodology. This will involve the use of a Scrum Board, Daily Stand-Up Meetings, Weekly Planning Meetings, Peer Review sessions and Version Control all as described below.


%----------------------------------------------------------------------------------------
%	DELIVERABLES SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	SCHEDULE SECTION
%----------------------------------------------------------------------------------------

\section{Schedule}

\subsection{Working Days}

Weekdays are designated as "Working Days".

On these days, the Group will meet briefly and be available for communication.

\subsection{Working Hours}

The hours between 09:00 and 23:00 (inclusive)  on Working Days are designated as Working Hours.

\subsection{Daily Stand-Up Meeting} 
Each member of the Group guarantees that they will make themselves available and present for at least \StandUpLength~at a daily stand up meeting on all Working Days. These meetings will occur at the following times and places:

\begin{center}
\begin{tabular}{c | c | c |}
\hline
Monday & 11:10 --- 11:35 & Telepresence \\
\hline
Tuesday & 13:00 --- 11:35 & Telepresence \\
\hline
Wednesday & 13:10 --- 13:35 & Telepresence \\
\hline
Thursday & 16:10 --- 16:35 & Telepresence \\
\hline
Friday & 14:10 --- 14:35 & Telepresence\\
\hline
\end{tabular}
\end{center}

During these meetings, every member of the Group will explain what they have finished, what they plan to finish and what impediments they face between stand-ups. 

If there is a written consensus between all members of the Group, a stand-up meeting can be skipped. This should only occur if no significant progress has been made towards completion of the Project and there are no impediments or dependencies that require discussion.


%----------------------------------------------------------------------------------------
%	TERMS AND CONDITIONS SECTION
%----------------------------------------------------------------------------------------

\section{Terms and Conditions}

\subsection{Communication}

All project-related communications shall occur via Facebook Messenger.

All members of the Group will read and respond (as necessary) to communications within 6 working hours of initial contact.

\subsection{Scrum Board}

The Scrum Board will be located at: \url{https://trello.com/b/...}

Proper usage of the Scrum Board requires:
\begin{itemize}
	\item User Stories are moved from the Product Backlog to the Sprint Backlog only at weekly planning meetings.
	\item User Stories are moved from the Sprint Backlog to the Current Stories before modifications are made to the relevant code.
	\item User Stories are returned to the Sprint Backlog if work stops due to a dependency issue or due to reassignment.
	\item Only one User Story is checked out at a time to any member of the Group.
	\item Comments are made on any User Story that is returned to the Sprint Backlog. These comments must indicate why the User Story has been returned and what must occur before work can resume.
	\item User Stories are moved into the Done section if and only if they meet the Definition of Done.
\end{itemize}

\subsection{Definition of Done}

In order for a user story or other module of code to be considered ``done'', the following conditions must be met in their entirety:
\begin{itemize}
\item The code must conform to the \_ Style Guide for \_
\item The code must pass testing with 90\% instruction coverage and according to all given specifications.
\item Unclear code is supplemented by concise internal documentation.
\item The code base is compile-able by... under...
\item The code has been peer reviewed.
\end{itemize}

\subsection{Version Control}

All Version Control of deliverables will be done with the Git repository located at: \\
\url{https://github.com/CSCD01/team_04-project}

%All commits will be signed by a GPG key associated with one of the above email
%addresses (listed above as ``developer emails'') via \url{https://keys.openpgp.org/} 
%and matching their github profile.

\subsection{Branching}

The Group agrees to the following branching strategy:

\begin{itemize}
\item DCMD: Don't commit to master, dummy
\item Merge only after peer review
\end{itemize}

\subsection{Continuity}

In the event that a member of the Group breaks adherence to this working agreement. 
\begin{enumerate}
	\item If tardiness is the cause of the breach, no strikes are recorded as long as 10 (fresh) Timbits are provided.
	\item If any more serious breaches of this contract occur, the individual(s) responsible will receive a strike on their record. Each such strike will be accompanied by a brief discussion between the offender and the Scrum Master (or another individual if the Scrum Master is the offender). The third strike will result in the escalation of the breach to the attention of the Client.
\end{enumerate}

\subsection{The Scrum Master}
The Scrum Master will be: 

The responsibilities of the Scrum Master will be:
\begin{itemize}
\item To lead each Daily Stand Up Meeting, Retrospective, and Planning Session and apportion time within to maximise productivity and cohesion.

\item To find assistance for any team member in distress with a specific and manageable Project-related impediment.

\item To discuss impediments and help redistribute labour at stand up meetings with each individual affected.

\item To keep a record of any strikes on the record of Group members, and if necessary report issues to the Client.
\end{itemize}

\subsection{Peer Review}
Review sessions will occur immediately following any stand-up after which there is code available for review and a reviewer available for sufficient time.

Both the reviewer and the writer of the new or modified code should be physically present and active during the review process. While the writer retains the power to ignore any suggested changes by the reviewer, a consensus is preferred.

\subsection{Planning Meetings}
A weekly planning meeting will be scheduled by the end of each Saturday. Such a meeting will occur in the first half of the week. The period between each planning meeting and the next is referred to as the sprint.

Planning meetings will include planning poker, to establish the expected time consumption of each new or modified user story in the Product Backlog. Correspondingly, story points will be assigned to each such story in the Scrum Board. Any stories still in the Sprint Backlog or Current Stories at the end of the sprint will be reassigned 0 story points.

The first planning meeting will establish this working agreement and predict an expected burn rate (number of story points completed per sprint). Successive meetings will begin with a review and recalculation of the burn rate.

Based on the current burn rate, and prioritization of user stories, the Sprint Backlog will be populated at the end of the planning meeting with user stories from the Product Backlog.


%----------------------------------------------------------------------------------------
%	ACCEPTANCE SECTION
%----------------------------------------------------------------------------------------

\newpage % Put signatures on a separate page

\section{Acceptance}

Any change to this contract shall be subject to a mutual written agreement of these parties.

The undersigned agrees to the terms of this agreement on behalf of his or her organization or business as of the date written below:

%------------------------------------------------

\subsection*{The Client} % Suppress section numbering with the *

\ClientName \\

\begin{tabular}{lp{10pt}l}
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Print Name: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Title: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \today
\end{tabular}

%------------------------------------------------

\subsection*{The Group} % Suppress section numbering with the *

\YourName \\

\begin{tabular}{ l p{10pt} l }
Signatures: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
&& \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
&& \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
&& \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \today
\end{tabular}

%----------------------------------------------------------------------------------------

\end{document}